Social Housing in Toronto

### 2024-04-22 paper/paper.qmd
commit

```{r}
#| label: data-overview
#| #| fig-cap: Data Overview
#| fig.pos: H
#| label: applications
#| fig-cap: Data Overview
#| echo: false

@@

>>>>

```{r}
#| label: data-overview
#| fig-cap: Data Overview
#| echo: false

@@

# Extract relevant columns with adjusted column names
year_quarter <- analysis_data$quarter_year
test <- analysis_data$total_active_waiting_list
inactive_cancelled <- analysis_data$inactive_cancelled
